\vspace{-.5cm} Lights: a generalized joint model for high-dimensional multivariate longitudinal data and censored durations \vspace{.5cm}

### 2022-01-31 manuscript/paper.tex
Update g functions

\subsection{\texttt{prox-QNMCEM class}}
\label{sec:prox-QNMCEM class}

Let us introduce the following useful notations
\begin{equation*}
  \left\{
    \begin{array}{ll}
    \tilde g^1&: b_i \mapsto b_i,\\
    \tilde g^2&: b_i \mapsto b_ib_i^\top, \\
    \tilde g^3_{s, k}&: b_i \mapsto \Psi_{k,i}(s), \\
    \tilde g^4_{s, \gamma_k}&: b_i \mapsto \exp \big\{\gamma_k^\top g^3_{s, k}(b_i) \big\}, \\
    \tilde g^5_{s, \gamma_k}&: b_i \mapsto g^3_{s, k}(b_i)^\top g^4_{s, k}(b_i).
    \end{array}
  \right. 
\end{equation*}
We also denote 
\[ \cI_1 = 
\begin{bmatrix}
  \ind{\{t_{1} = t_1^u\}}  & \cdots & \ind{\{t_{1} = t_J^u\}}\\
  \vdots &  \ddots & \vdots \\
  \ind{\{t_{n} = t_1^u\}} & \cdots & \ind{\{t_{n} = t_J^u\}}
\end{bmatrix}
\in \R^{n \times J}
\quad \text{and} \quad 
\cI_2 = 
\begin{bmatrix}
  \ind{\{t_{1} \leq t_1^u\}} & \cdots & \ind{\{t_{1} \leq t_J^u\}}\\
  \vdots &  \ddots & \vdots \\
  \ind{\{t_{n} \leq t_1^u\}} & \cdots & \ind{\{t_{n} \leq t_J^u\}}
\end{bmatrix}
\in \R^{n \times J} \]
some matrices to compare each event times with the vector of distinct event times. Those matrices are widely used in practice to replace indicators. For instance, the quantities
\begin{align*}
f(t_i, \delta_i| \breve{b}, G_i = k ; \theta^{(w)}) = &\big(\lambda_0^{(w)}(t_i) g^4_{t_i, \gamma_k^{(w)}}(\breve{b}) \big)^{\delta_i} \\ 
&\times \exp \Big\{ - \sum_{j=1}^J \lambda_0^{(w)}(t_j^u) g^4_{t_j^u, \gamma_k^{(w)}}(\breve{b}) \ind{\{t_j^u \leq t_i\}} \Big\}
\end{align*}
for $i = 1, \ldots, n$ and $\breve{b} \in S^{(w)}$ can be represented in the following matrix 
\[ \underset{J}{\text{sum}} \big( \boldsymbol{g^4_{\gamma_k}} \boldsymbol{\lambda_0^{(w)}} \cI_1 \big)^{\boldsymbol{\delta}} \exp \big\{- \underset{J}{\text{sum}} \big(\boldsymbol{g^4_{\gamma_k}} \boldsymbol{\lambda_0^{(w)}} \cI_2 \big) \big\} \in \R^{n \times 2N} \]
where 
\begin{equation*}
  \left\{
    \begin{array}{ll}
    \boldsymbol{g^4_{\gamma_k}} \in \R^{2N \times J} \text{ with } \big[\boldsymbol{g^4_{\gamma_k}}\big]_{i, j} = \tilde g^4_{t_j^u, \gamma_k^{(w)}}(\breve{b}_i) , \\
    \boldsymbol{\lambda_0^{(w)}} = \big(\lambda_0^{(w)}(t_1^u), \ldots, \lambda_0^{(w)}(t_J^u) \big)^\top \in \R^J, \\
    \boldsymbol{\delta} = (\delta_1, \ldots, \delta_n)^\top \in \R^n.
    \end{array}
  \right.
\end{equation*}
Another example is the update of the baseline hazard~\eqref{eq:update_lambda_0} as
\[\boldsymbol{\lambda_0^{(w+1)}} = \underset{n}{\text{sum}}( \boldsymbol{\delta} \cI_1) / \underset{n}{\text{sum }} \underset{k}{\text{sum }} (\boldsymbol{g^4_{\gamma_k}} \cI_2 \boldsymbol{\hat \pi^{(w)}})\]
with $\boldsymbol{\hat \pi^{(w)}} \in \R^{2 \times n} \text{ and }  \left\{
    \begin{array}{ll}
    \boldsymbol{\hat \pi_{1,\bullet}^{(w)}}= (\hat \pi_{11}^{\theta^{(w)}}, \ldots, \hat \pi_{n1}^{\theta^{(w)}})^\top \in \R^n, \\
    \boldsymbol{\hat\pi_{0,\bullet}^{(w)}} = 1 - \boldsymbol{\hat\pi_{1,\bullet}^{(w)}}.
    \end{array}
  \right.$

>>>>

\subsection{\texttt{prox-QNEM class}}
\label{sec:prox-QNEM class}

Let us introduce the following useful notations
\begin{equation*}
  \left\{
    \begin{array}{ll}
    \tilde g^1&: b_i \mapsto b_i,\\
    \tilde g^2&: b_i \mapsto b_ib_i^\top.
    \end{array}
  \right. 
\end{equation*}
